Rewind: Automatically Generated\\Digital Memories from Mobile Geolocation Data

### 2016-09-19 paper/uist_2016/paper.tex
before major changes

\section{User Study}
\subsection{Research Questions}
The Rewind system enables us to ask questions about people's attitudes and behaviors surrounding digital memories that were not possible to answer before due to the scarcity of comprehensive data about where a person has been. To understand what makes a digital memory meaningful to a person, we performed a within-subjects comparison of Rewinds and static photos. By comparing Rewinds to today's most prevalent form of digital memory media, we can distill what features make a Rewind meaningful and representative as a memory of a trip.

Our research questions examine the effectiveness of Rewinds through three virtues of a memory: memorability, believability, and desirability.

\begin{enumerate}
\item Memorability: Do certain features of a location or trip depicted in a digital memory make the memory more recallable? 
\item Believability:  Is the digital memory accurate to the participant's memory? What features make a digital memory accurate or inaccurate?
\item Desirability: Which digital memories do users wish to save? Do certain features make a digital memory more likely to be kept?
\end{enumerate}

\subsection{Participants}
To recruit a diverse local population, participants for the user study were recruited online through local forums (Craigslist classifieds and local Reddit communities). Offline, ads were posted in cafes and other small businesses in the the city. Of the 21 total participants, 13 identified as men and 8 identified as women, and ranged from 20 to 50 years old. Participants were mainly local residents, with occupations including librarian, medical researcher, office worker, IT consultant, student, musician, and comedian.
% Jeff notes, comment this out because it's not remarkable
% A fifth of the participants were undergraduate or graduate students.

\subsection{Procedure}
Participants underwent a two-week tracking period followed by a mixed-methods user study which investigated the memorability, believability, and desirability of the Rewinds produced from the two weeks of location data.

@@

The participant was then shown a Rewind of the trip that they were on when the previous location was encountered. While the Rewind was playing, the participant could hover over the Rewind panel and scrub backwards and forwards horizontally through the images that composed the video. This allowed participants to ``walk through'' their memory at their own pace. The participant was asked the following questions while the Rewind played: Do you remember these locations? Do you remember this particular trip? Can  you name some of the streets? Can you name what is around these locations, such as buildings, landmarks, or other places? Would you want to keep this video? Why or why not? Were you traveling alone? If you remember these locations, is the video accurate to your memory? Why or why not? What was different?

@@

Data from three participants was not included in the results of this study. One of the participants' data points consisted of only one location. The participant used a mobile device provided by the study, so it is likely that they did not carry the device on their person. Another participant did not complete the in-person interview portion of the user study due to health and scheduling reasons. The last participant only collected three days of data because they had their phone replaced during the tracking period, and did not reactivate Google's location reporting services on their new device. This participant completed the in-person interview portion of the user study, but we did not include the data gathered during this participant's session in the results.

\section{Findings}
The findings of our user study center on the participants' relationship to the Rewinds generated from their location data. We focus on the participants' judgments of their Rewinds' memorability, believability, and desirability in comparison to their judgments of the photos paired with the Rewinds. We also discuss the participants' interactions with and reactions to their Rewinds. The results use data from the user studies conducted with 12 men and 6 women. Half of the participants identified themselves as frequent travelers. Additionally, half of the participants were regular GPS users, that is people who used GPS even in locations already familiar to them.

@@

			\multicolumn{1}{c}{}                                 & \multicolumn{1}{c}{}                         & \multicolumn{1}{c|}{}      & \multicolumn{2}{c|}{GPS usage}                                                                                       & \multicolumn{2}{c|}{Traveller type}                                                                                  & \multicolumn{2}{c|}{Accompany}                                                                                               & \multicolumn{6}{c|}{Distance}                                                                                                                                                                                                                                                                                                            & \multicolumn{2}{c|}{Visit frequency}                                                                                 \\ \cline{4-17} 

>>>>

\section{User Study}
% this needs to be polished
\subsection{Research Questions}
% is "digital memory" the right phrase for describing Rewind? Isn't rewind a medium for providing the cues to retrieve exisiting memories rather than creating new memories?
\textit{Rewind} enables us to ask questions about people's attitudes and behaviors surrounding digital memories that were not possible to answer before due to the scarcity of comprehensive data about where a person has been. To understand what makes a digital memory meaningful to a person, we performed a within-subjects comparison of Rewinds and static photos. By comparing Rewinds to today's most prevalent form of digital memory media, we can distill what features make a Rewind meaningful and representative as a memory of a trip.

Our research questions examine the effectiveness of \textit{Rewind} videos through three virtues of a memory: memorability, believability, and desirability. %do we need a reference for the three virtues?

% best way to put it?
\begin{enumerate}
\item Memorability: How would \textit{Rewind} facilitate the retrival of episodic memory? What types of users are most likely to recall their memories using \textit{Rewind}?
\item Believability:  How accurate are \textit{Rewind} artifacts in the eyes of the users' ? 
\item Desirability: What factors are inherent to users' decisions in preserving artifacts created by \textit{Rewind}?
\end{enumerate}

% where to put this part or do we need a summary like this at all?
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Our user study explored the following five metrics that could potentially influence the aforesaid three measurements of \textit{Rewind} vidoes. These five metrics are:
\begin{enumerate}
\item GPS usage: how self-identified regular GPS users and non-regular GPS users differ in their responses to \textit{Rewind} videos.
\item Traveler type: how self-identified frequent travelers and non-frequent travelers report to the three measurements of \textit{Rewind} videos differently.
\item Companions: how traveling companionship and solitude affect users' viewpoints on \textit{Rewind} videos.
\item Distance: how traveling distances affect users' perceptions of \textit{Rewind} videos.
\item Visit frequency: how visit frequency of a particular place influence users' reporting on \textit{Rewind} videos.
\end{enumerate}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Participants}
To recruit a diverse local population, participants for the user study were recruited online through local forums (Craigslist classifieds and local Reddit communities). Offline, ads were posted in cafes and other small businesses in the the city. Of the 21 total participants, 13 were identified as men and 8 were identified as women, with age ranged from 20 to 50 years old. Participants were mainly local residents, with occupations including librarian, medical researcher, office worker, IT consultant, student, musician, and comedian.
% Jeff notes, comment this out because it's not remarkable
% A fifth of the participants were undergraduate or graduate students.

\subsection{Procedure}
Participants underwent a two-week tracking period followed by a mixed-methods user study which investigated the memorability, believability, and desirability of \textit{Rewind} artifacts produced from the two weeks of location data.

@@

% Rewind of the trip or Rewind video of the trip?
The participant was then shown a Rewind of the trip that they were on when the previous location was encountered. While the Rewind was playing, the participant could hover over the Rewind panel and scrub backwards and forwards horizontally through the images that composed the video. This allowed participants to ``walk through'' their memory at their own pace. The participant was asked the following questions while the Rewind played: Do you remember these locations? Do you remember this particular trip? Can  you name some of the streets? Can you name what is around these locations, such as buildings, landmarks, or other places? Would you want to keep this video? Why or why not? Were you traveling alone? If you remember these locations, is the video accurate to your memory? Why or why not? What was different?

@@

% ...that they did not carry the device on their person. - grammatical error?
Data from three participants was not included in the results of this study. One of the participants' data points consisted of only one location. The participant used a mobile device provided by the study, so it is likely that they did not carry the device on their person. Another participant did not complete the in-person interview portion of the user study due to health and scheduling reasons. The last participant only collected three days of data because they had their phone replaced during the tracking period, and did not reactivate Google's location reporting services on their new device. This participant completed the in-person interview portion of the user study, but we did not include the data gathered during this participant's session in the results.

% need to be rephrased.
\section{Findings}
Our user study explored five metrics that could potentially affect participants' memorability, belivability, and desirability of \textit{Rewind} vidoes. These five metrics are:

participants' relationship to \textit{Rewind} videos generated from their location data. We focus on the participants' judgments of their Rewinds' memorability, believability, and desirability in comparison to their judgments of the photos paired with the Rewinds. We also discuss the participants' interactions with and reactions to their Rewinds. The results use data from the user studies conducted with 12 men and 6 women. Half of the participants identified themselves as frequent travelers. Additionally, half of the participants were regular GPS users, that is people who used GPS even in locations already familiar to them.

@@

			\multicolumn{1}{c}{}                                 & \multicolumn{1}{c}{}                         & \multicolumn{1}{c|}{}      & \multicolumn{2}{c|}{GPS usage}                                                                                       & \multicolumn{2}{c|}{Traveller type}                                                                                  & \multicolumn{2}{c|}{Companions}                                                                                               & \multicolumn{6}{c|}{Distance}                                                                                                                                                                                                                                                                                                            & \multicolumn{2}{c|}{Visit frequency}                                                                                 \\ \cline{4-17} 
